---
title: "Data analysis for Number of CTs and Xist Histogram"
author: "Ziad Jowhar and Sigal Shachar"
date: "June 04 2018"
output:
  html_document: default
  pdf_document: default
---

### Introduction

This script analyzes data obtained by imaging primary human fibroblasts stained with chromosome paints for chr X (green channel), Y (Red channel), 18 (Red channel), and Xist (Far Red channel). Cells were grown in PE-cellCarrierUltra 384 plates and imaged using the YOKOGAWA CV7000 microscope with a 40X-air objective. Images were imported into KNIME and analyzed and the results were exported as tab separated csv files.
The script reads the csv files and calculates the Number of CTs per nucleus.

Load packages.
```{r packages}
library('plyr')
library('dplyr')
library('ggplot2')
library('stringr')
library('knitr')
library('SpatialTools')
library('reshape2')
library('DT')
library('data.table')
library('Hmisc')
library('scales')
```

#Chunk 1 
EXP27p1-EXP27p2-EXP28p1-EXP28p2-EXP30p3-EXP30p4 - Chromosome X and Y and Xist Data 
```{r X - Y - Xist ReadCsvFiles}
#EXP27p1
FR_Data_27p1_Xist <- fread(file="./XistXY_CTSeg_Tables/27p1/180503_EXP27p1_XistXY_CTSeg/gudlap/20180507_140523/AllWells_FarRedProbeMeasurements_FilteredByNucleiXExpectedCount.csv", check.names = T, showProgress = T)

R_Data_27p1_Y <- fread(file="./XistXY_CTSeg_Tables/27p1/180503_EXP27p1_XistXY_CTSeg/gudlap/20180507_140523/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

G_Data_27p1_X <- fread(file="./XistXY_CTSeg_Tables/27p1/180503_EXP27p1_XistXY_CTSeg/gudlap/20180507_140523/GreenCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
FR_Data_27p1_Xist$EXPPlate<- "Exp27p1"
R_Data_27p1_Y$EXPPlate<- "Exp27p1"
G_Data_27p1_X$EXPPlate<- "Exp27p1"

################

#EXP27p2
FR_Data_27p2_Xist <- fread(file="./XistXY_CTSeg_Tables/27p2/180503_EXP27p2_XistXY_CTSeg/gudlap/20180507_153512/AllWells_FarRedProbeMeasurements_FilteredByNucleiXExpectedCount.csv", check.names = T, showProgress = T)

R_Data_27p2_Y <- fread(file="./XistXY_CTSeg_Tables/27p2/180503_EXP27p2_XistXY_CTSeg/gudlap/20180507_153512/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

G_Data_27p2_X <- fread(file="./XistXY_CTSeg_Tables/27p2/180503_EXP27p2_XistXY_CTSeg/gudlap/20180507_153512/GreenCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
FR_Data_27p2_Xist$EXPPlate<- "Exp27p2"
R_Data_27p2_Y$EXPPlate<- "Exp27p2"
G_Data_27p2_X$EXPPlate<- "Exp27p2"

################

#EXP28p1
FR_Data_28p1_Xist <- fread(file="./XistXY_CTSeg_Tables/28p1/180503_EXP28p1_XistXY_CTSeg/gudlap/20180507_173900/AllWells_FarRedProbeMeasurements_FilteredByNucleiXExpectedCount.csv", check.names = T, showProgress = T)

R_Data_28p1_Y <- fread(file="./XistXY_CTSeg_Tables/28p1/180503_EXP28p1_XistXY_CTSeg/gudlap/20180507_173900/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

G_Data_28p1_X <- fread(file="./XistXY_CTSeg_Tables/28p1/180503_EXP28p1_XistXY_CTSeg/gudlap/20180507_173900/GreenCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
FR_Data_28p1_Xist$EXPPlate<- "Exp28p1"
R_Data_28p1_Y$EXPPlate<- "Exp28p1"
G_Data_28p1_X$EXPPlate<- "Exp28p1"

################

#EXP28p2
FR_Data_28p2_Xist <- fread(file="./XistXY_CTSeg_Tables/28p2/180503_EXP28p2_XistXY_CTSeg/gudlap/20180507_210107/AllWells_FarRedProbeMeasurements_FilteredByNucleiXExpectedCount.csv", check.names = T, showProgress = T)

R_Data_28p2_Y <- fread(file="./XistXY_CTSeg_Tables/28p2/180503_EXP28p2_XistXY_CTSeg/gudlap/20180507_210107/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

G_Data_28p2_X <- fread(file="./XistXY_CTSeg_Tables/28p2/180503_EXP28p2_XistXY_CTSeg/gudlap/20180507_210107/GreenCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
FR_Data_28p2_Xist$EXPPlate<- "Exp28p2"
R_Data_28p2_Y$EXPPlate<- "Exp28p2"
G_Data_28p2_X$EXPPlate<- "Exp28p2"

################

#EXP30p3
FR_Data_30p3_Xist <- fread(file="./XistXY_CTSeg_Tables/30p3/180503_EXP30p3_XistXY_CTSeg/gudlap/20180507_153512/AllWells_FarRedProbeMeasurements_FilteredByNucleiXExpectedCount.csv", check.names = T, showProgress = T)

R_Data_30p3_Y <- fread(file="./XistXY_CTSeg_Tables/30p3/180503_EXP30p3_XistXY_CTSeg/gudlap/20180507_153512/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

G_Data_30p3_X <- fread(file="./XistXY_CTSeg_Tables/30p3/180503_EXP30p3_XistXY_CTSeg/gudlap/20180507_153512/GreenCT_Count_PerNucleus.csv", check.names = T, showProgress = T)
#Add New Plate Column#
FR_Data_30p3_Xist$EXPPlate<- "Exp30p3"
R_Data_30p3_Y$EXPPlate<- "Exp30p3"
G_Data_30p3_X$EXPPlate<- "Exp30p3"

################

#EXP30p4
FR_Data_30p4_Xist <- fread(file="./XistXY_CTSeg_Tables/30p4/180503_EXP30p4_XistXY_CTSeg/gudlap/20180507_173901/AllWells_FarRedProbeMeasurements_FilteredByNucleiXExpectedCount.csv", check.names = T, showProgress = T)

R_Data_30p4_Y <- fread(file="./XistXY_CTSeg_Tables/30p4/180503_EXP30p4_XistXY_CTSeg/gudlap/20180507_173901/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

G_Data_30p4_X <- fread(file="./XistXY_CTSeg_Tables/30p4/180503_EXP30p4_XistXY_CTSeg/gudlap/20180507_173901/GreenCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
FR_Data_30p4_Xist$EXPPlate<- "Exp30p4"
R_Data_30p4_Y$EXPPlate<- "Exp30p4"
G_Data_30p4_X$EXPPlate<- "Exp30p4"



```

#Chunk 2 
Merge 27-30 (6plates) - Chromosome X and Y and Xist Data
```{r X - Y - Xist MergeCsvFiles}

#Merge EXP 27-30 XYXist
FR_Xist_AllEXP<- rbind(FR_Data_27p1_Xist, FR_Data_27p2_Xist, FR_Data_28p1_Xist, FR_Data_28p2_Xist, FR_Data_30p3_Xist, FR_Data_30p4_Xist)
R_Y_AllEXP<- rbind(R_Data_27p1_Y, R_Data_27p2_Y, R_Data_28p1_Y, R_Data_28p2_Y, R_Data_30p3_Y, R_Data_30p4_Y)
G_X_AllEXP<- rbind(G_Data_27p1_X, G_Data_27p2_X, G_Data_28p1_X, G_Data_28p2_X, G_Data_30p4_X, G_Data_30p4_X)

```

#Chunk 3 
Merge 11-30 (10 plates) - Chromosome 18 Data 
```{r CT 18 ReadCsvFiles}
################ Chr.18

#Exp 11p1
R_Data_11p1_18 <- fread(file= "./XY18_CTSeg_Tables/11p1/180503_EXP11p1_18XY_CTSeg/gudlap/20180503_175052/RedCT_Count_PerNucleus.csv")
setnames(R_Data_11p1_18, old=c("row ID", "Common Filename", "Parent folder", "File extension", "Well Position", "TimePoint", "FieldNumber",  "Green Probe",  "Red Probe", "Far Red Probe", "Green Probe Detect", "Red Probe Detect", "Far Red Probe Detect", "Karyotype", "Patient ID", "NucleusID", "Number of Unique Labels", "Probe Color"), new=c("row.ID", "Common.Filename", "Parent.folder", "File.extension", "Well.Position", "TimePoint", "FieldNumber", "Green.Probe", "Red.Probe", "Far.Red.Probe", "Green.Probe.Detect", "Red.Probe.Detect", "Far.Red.Probe.Detect", "Karyotype", "Patient.ID", "NucleusID", "Number.of.Unique.Labels", "Probe.Color"))

#Add New Plate Column#
R_Data_11p1_18$EXPPlate<- "11p1"

################

#Exp 12p2
R_Data_12p2_18 <- fread(file="./XY18_CTSeg_Tables/12p2/180503_EXP12p2_18XY_CTSeg/gudlap/20180508_134010/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)
R_Data_12p2_18 <- subset(R_Data_12p2_18, Well.Position != " C07" & Well.Position != " C08" & Well.Position != " C09" & Well.Position != " D07" & Well.Position != " D08" & Well.Position != " D09" )

#Add New Plate Column#
R_Data_12p2_18$EXPPlate<- "12p2"

################

#Exp 14p1
R_Data_14p1_18 <- fread(file="./XY18_CTSeg_Tables/14p1_40X/180503_EXP14p1_18XY_CTSeg/gudlap/20180504_172619/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)
R_Data_14p1_18$Karyotype[R_Data_14p1_18$Karyotype=='X'] <- "XO" 
R_Data_14p1_18_XY <- subset(R_Data_14p1_18, Karyotype != "XY")

#Add New Plate Column#
R_Data_14p1_18$EXPPlate<- "14p1"

################

#Exp 17p1
R_Data_17p1_18 <- fread(file="./XY18_CTSeg_Tables/17p1/180503_EXP17p1_18XY_CTSeg/gudlap/20180504_165334/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)
R_Data_17p1_18$Karyotype[R_Data_17p1_18$Karyotype=='X'] <- "XO" 
R_Data_17p1_18_XY <- subset(R_Data_17p1_18, Karyotype != "XY")

#Add New Plate Column#
R_Data_17p1_18$EXPPlate<- "17p1"

################

#Exp 20p2
R_Data_20p2_18 <- fread(file="./XY18_CTSeg_Tables/20p2/180503_EXP20p2_18XY_CTSeg/gudlap/20180504_164359/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)
R_Data_20p2_18 <- subset(R_Data_20p2_18, Well.Position != " E06" & Well.Position != " E07" & Well.Position != " E08" & Well.Position != " F06" & Well.Position != " F07" & Well.Position != " F08" )

#Add New Plate Column#
R_Data_20p2_18$EXPPlate<- "20p2"

################

#Exp 22p1
R_Data_22p1_18 <- fread(file="./XY18_CTSeg_Tables/22p1/180503_EXP22p1_18XY_CTSeg/gudlap/20180503_211017/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)
R_Data_22p1_18 <- subset(R_Data_22p1_18, Well.Position != " E06" & Well.Position != " E07" & Well.Position != " E08" & Well.Position != " F06" & Well.Position != " F07" & Well.Position != " F08" & Well.Position != " G06" & Well.Position != " G07" & Well.Position != " G08" )

#Add New Plate Column#
R_Data_22p1_18$EXPPlate<- "22p1"

################

#Exp 27p1
R_Data_27p1_18 <- fread(file="./XY18_CTSeg_Tables/27p1_18XY/180503_EXP27p1_18XY_CTSeg/gudlap/20180503_221059/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
R_Data_27p1_18$EXPPlate<- "27p1"

###########

#EXP27p2
R_Data_27p2_18 <- fread(file="./XY18_CTSeg_Tables/27p2_18XY/180522_EXP27p2_18XY_CTSeg/jowharzm/20180522_144855/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
R_Data_27p2_18$EXPPlate<- "27p2"

################

#Exp 28p1
R_Data_28p1_18 <- fread(file="./XY18_CTSeg_Tables/28p1_18XY/180503_EXP28p1_18XY_CTSeg/gudlap/20180504_074216/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
R_Data_28p1_18$EXPPlate<- "28p1"

################

#Exp 30p1
R_Data_30p1_18 <- fread(file="./XY18_CTSeg_Tables/30p1_18XY/180503_EXP30p1_18XY_CTSeg/gudlap/20180504_112257/RedCT_Count_PerNucleus.csv", check.names = T, showProgress = T)

#Add New Plate Column#
R_Data_30p1_18$EXPPlate<- "30p1"


```

#Chunk 4 
Merge 11-30 (6plates) - Chromosome 18 Data 
```{r CT 18 MergeCsvFiles}

#Merge EXP 11-30 Chr 18
R_18_AllEXP<- rbind(R_Data_11p1_18, R_Data_12p2_18, R_Data_14p1_18, R_Data_17p1_18, R_Data_20p2_18, R_Data_22p1_18, R_Data_27p1_18,  R_Data_27p2_18, R_Data_28p1_18, R_Data_30p1_18)

```

#Chunk 5
Labeling of the patient number for all patients and merging. 
```{r Identify Patient NumberCTs}
#PATIENT 1
G_X_PATIENT1 <- G_X_AllEXP [Patient.ID == "FA" , ] 

R_Y_PATIENT1 <- R_Y_AllEXP [Patient.ID == "FA" , ]

R_18_PATIENT1 <- R_18_AllEXP [Patient.ID == "FA" , ]

FR_Xist_PATIENT1 <- FR_Xist_AllEXP [Patient.ID == "FA" , ]

G_X_PATIENT1$PatientNumber<- "1"
R_Y_PATIENT1$PatientNumber<- "1"
R_18_PATIENT1$PatientNumber<- "1"
FR_Xist_PATIENT1$PatientNumber<- "1"

#PATIENT 2
G_X_PATIENT2 <- G_X_AllEXP [Patient.ID == "FB" , ]

R_Y_PATIENT2 <- R_Y_AllEXP [Patient.ID == "FB" , ]

R_18_PATIENT2 <- R_18_AllEXP [Patient.ID == "FB" , ]

FR_Xist_PATIENT2 <- FR_Xist_AllEXP [Patient.ID == "FB" , ]

G_X_PATIENT2$PatientNumber<- "2"
R_Y_PATIENT2$PatientNumber<- "2"
R_18_PATIENT2$PatientNumber<- "2"
FR_Xist_PATIENT2$PatientNumber<- "2"

#PATIENT 3
G_X_PATIENT3 <- G_X_AllEXP [Patient.ID == "FC" , ]

R_Y_PATIENT3 <- R_Y_AllEXP [Patient.ID == "FC" , ]

R_18_PATIENT3 <- R_18_AllEXP [Patient.ID == "FC" , ]

FR_Xist_PATIENT3 <- FR_Xist_AllEXP [Patient.ID == "FC" , ] 

G_X_PATIENT3$PatientNumber<- "3"
R_Y_PATIENT3$PatientNumber<- "3"
R_18_PATIENT3$PatientNumber<- "3"
FR_Xist_PATIENT3$PatientNumber<- "3"

####All Data with patient batch
AllG_X <- rbind(G_X_PATIENT1, G_X_PATIENT2, G_X_PATIENT3)
AllR_Y <- rbind(R_Y_PATIENT1, R_Y_PATIENT2, R_Y_PATIENT3)
AllR_18 <- rbind(R_18_PATIENT1, R_18_PATIENT2, R_18_PATIENT3)
AllFR_Xist <- rbind(FR_Xist_PATIENT1, FR_Xist_PATIENT2, FR_Xist_PATIENT3)

################

```

#Chunk 6
Number of CTs per nucleus per karyotypes for chromosomes 18, X, and Y and Xist.
```{r Percentage of 18 - X - Y CTs or Xist Foci per nuclei per karyotype}
############## G - X

XCT_df <- data.frame(data.frame(Number.of.CT=AllG_X$Number.of.Unique.Labels,
                                Karyotype=AllG_X$Karyotype, 
                                PatientNumber = AllG_X$PatientNumber, 
                                EXPPlate = AllG_X$EXPPlate))

XCT_df1 <- XCT_df %>% 
       dplyr::group_by(Number.of.CT, Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::summarise(n=n()) %>%  
       dplyr::group_by(Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::mutate(perc=100*n/sum(n))%>% 
       dplyr::group_by(Karyotype, Number.of.CT) %>%
       dplyr::summarise(mean_perc = mean(perc, na.rm = TRUE),
                 sd_perc = sd(perc, na.rm = TRUE),
                 ymax = (mean_perc + sd_perc),
                 ymin = (mean_perc - sd_perc))

XCT <- ggplot(XCT_df1, aes(x=Number.of.CT, y=mean_perc)) +
  geom_bar(stat="identity", fill = "#56B4E9", color = "#999999", width = 0.7) +
  labs(title = "X Chromosome")+
  xlab('Number of CTs per Cell') + 
  ylab("Percent") + 
  coord_cartesian(xlim = c(0,5))+
  scale_x_continuous(breaks = 0:5) +
  scale_y_continuous(limits = c(0, 100))+
  geom_errorbar(aes(ymin = ymin,
                    ymax= ymax), 
                    colour="black", 
                    width = 0.2,
                    position = position_dodge(width = 0.9))+
  facet_wrap(~ Karyotype, ncol=3)+
  theme_bw()+
  theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 20), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 

XCT

############## R - Y

YCT_df <- data.frame(data.frame(Number.of.CT=AllR_Y$Number.of.Unique.Labels, 
                                Karyotype=AllR_Y$Karyotype, 
                                PatientNumber = AllR_Y$PatientNumber, 
                                EXPPlate = AllR_Y$EXPPlate))

YCT_df1 <- YCT_df %>% 
       dplyr::group_by(Number.of.CT, Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::summarise(n=n()) %>%  
       dplyr::group_by(Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::mutate(perc=100*n/sum(n))%>% 
       dplyr::group_by(Karyotype, Number.of.CT) %>%
       dplyr::summarise(mean_perc = mean(perc, na.rm = TRUE),
                 sd_perc = sd(perc, na.rm = TRUE),
                 ymax = (mean_perc + sd_perc),
                 ymin = (mean_perc - sd_perc))

YCT <- ggplot(YCT_df1, aes(x=Number.of.CT, y=mean_perc)) +
  geom_bar(stat="identity", fill = "#56B4E9", color = "#999999", width = 0.7) +
  labs(title = "Y Chromosome")+
  xlab('Number of CTs per Cell') + 
  ylab("Percent") + 
  coord_cartesian(xlim = c(0,5))+
  scale_x_continuous(breaks = 0:5) +
  scale_y_continuous(limits = c(0, 100))+
  geom_errorbar(aes(ymin = ymin,
                    ymax= ymax), 
                    colour="black", 
                    width = 0.2,
                    position = position_dodge(width = 0.9))+
  facet_wrap(~ Karyotype, ncol=2)+
  theme_bw()+
  theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 20), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 

YCT

############## R - 18

CT18_df <- data.frame(data.frame(Number.of.CT=AllR_18$Number.of.Unique.Labels,
                                 Karyotype=AllR_18$Karyotype, 
                                 PatientNumber = AllR_18$PatientNumber, 
                                 EXPPlate = AllR_18$EXPPlate))

CT18_df1 <- CT18_df %>% 
       dplyr::group_by(Number.of.CT, Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::summarise(n=n()) %>%  
       dplyr::group_by(Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::mutate(perc=100*n/sum(n))%>% 
       dplyr::group_by(Karyotype, Number.of.CT) %>%
       dplyr::summarise(mean_perc = mean(perc, na.rm = TRUE),
                 sd_perc = sd(perc, na.rm = TRUE),
                 ymax = (mean_perc + sd_perc),
                 ymin = (mean_perc - sd_perc))

CT18 <- ggplot(CT18_df1, aes(x=Number.of.CT, y=mean_perc)) +
  geom_bar(stat="identity", fill = "#56B4E9", color = "#999999", width = 0.7) +
  labs(title = "Chromosome 18")+
  xlab('Number of CTs per Cell') + 
  ylab("Percent") + 
  coord_cartesian(xlim = c(0,5))+
  scale_x_continuous(breaks = 0:5) +
  scale_y_continuous(limits = c(0, 100))+
  geom_errorbar(aes(ymin = ymin,
                    ymax= ymax), 
                    colour="black", 
                    width = 0.2,
                    position = position_dodge(width = 0.9))+
  facet_wrap(~ Karyotype, ncol=3)+
  theme_bw()+
  theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 20), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 

CT18

############## FR - Xist - All Karyotypes 

Xist_df <- data.frame(data.frame(Number.of.CT=AllFR_Xist$Number.of.Unique.Labels, 
                                Karyotype=AllFR_Xist$Karyotype, 
                                PatientNumber = AllFR_Xist$PatientNumber, 
                                EXPPlate = AllFR_Xist$EXPPlate))

Xist_df1 <- Xist_df %>% 
       dplyr::group_by(Number.of.CT, Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::summarise(n=n()) %>%  
       dplyr::group_by(Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::mutate(perc=100*n/sum(n))%>% 
       dplyr::group_by(Karyotype, Number.of.CT) %>%
       dplyr::summarise(mean_perc = mean(perc, na.rm = TRUE),
                 sd_perc = sd(perc, na.rm = TRUE),
                 ymax = (mean_perc + sd_perc),
                 ymin = (mean_perc - sd_perc))

Xist <- ggplot(Xist_df1, aes(x=Number.of.CT, y=mean_perc)) +
  geom_bar(stat="identity", fill = "#56B4E9", color = "#999999", width = 0.7) +
  labs(title = "Xist Foci")+
  xlab('Number of Xist Foci per Cell') + 
  ylab("Percent") + 
  coord_cartesian(xlim = c(0,5))+
  scale_x_continuous(breaks = 0:5) +
  scale_y_continuous(limits = c(0, 100))+
  geom_errorbar(aes(ymin = ymin,
                    ymax= ymax), 
                    colour="black", 
                    width = 0.2,
                    position = position_dodge(width = 0.9))+
  facet_wrap(~ Karyotype, ncol=3)+
  theme_bw()+
  theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 20), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 

Xist

############## FR - XiST - MultiX cells only - All Three Patients Combined

AllFR_Xist_MultiX <- AllFR_Xist[Karyotype == "XX" | Karyotype == "XXX" | Karyotype == "XXXX" | Karyotype == "XXXXY" | Karyotype == "XXY" | Karyotype == "XXYY" , ]

MultiX_Xist_df <- data.frame(data.frame(Number.of.CT=AllFR_Xist_MultiX$Number.of.Unique.Labels, 
                                Karyotype=AllFR_Xist_MultiX$Karyotype, 
                                PatientNumber = AllFR_Xist_MultiX$PatientNumber, 
                                EXPPlate = AllFR_Xist_MultiX$EXPPlate))

MultiX_Xist_df1 <- MultiX_Xist_df %>% 
       dplyr::group_by(Number.of.CT, Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::summarise(n=n()) %>%  
       dplyr::group_by(Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::mutate(perc=100*n/sum(n))%>% 
       dplyr::group_by(Karyotype, Number.of.CT) %>%
       dplyr::summarise(mean_perc = mean(perc, na.rm = TRUE),
                 sd_perc = sd(perc, na.rm = TRUE),
                 ymax = (mean_perc + sd_perc),
                 ymin = (mean_perc - sd_perc))

MultiX_Xist <- ggplot(MultiX_Xist_df1, aes(x=Number.of.CT, y=mean_perc)) +
  geom_bar(stat="identity", fill = "#56B4E9", color = "#999999", width = 0.7) +
  xlab('Number of Xist CTs per Cell') + 
  ylab("Percent (%)") + 
  coord_cartesian(xlim = c(0,5))+
  scale_x_continuous(breaks = 0:5) +
  scale_y_continuous(limits = c(0, 100))+
  geom_errorbar(aes(ymin = ymin,
                    ymax= ymax), 
                    colour="black", 
                    width = 0.2,
                    position = position_dodge(width = 0.9))+
  facet_wrap(~ Karyotype, ncol=2)+
  theme_bw()+
  theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 20), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 

MultiX_Xist

############## FR - XiST - MultiX cells only - All Three Patients

MultiX_Xist_df2 <- MultiX_Xist_df %>% 
       dplyr::group_by(Number.of.CT, Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::summarise(n=n()) %>%  
       dplyr::group_by(Karyotype, PatientNumber, EXPPlate) %>%  
       dplyr::mutate(perc=100*n/sum(n))%>% 
       dplyr::group_by(Karyotype, PatientNumber, Number.of.CT) %>%
       dplyr::summarise(mean_perc = mean(perc, na.rm = TRUE),
                 sd_perc = sd(perc, na.rm = TRUE),
                 ymax = (mean_perc + sd_perc),
                 ymin = (mean_perc - sd_perc))

MultiX_Xist_2 <- ggplot(MultiX_Xist_df2, aes(x=Number.of.CT, y=mean_perc)) +
  geom_bar(stat="identity", fill = "#56B4E9", color = "#999999", width = 0.7) +
  labs(title = "Xist Foci")+
  xlab('Number of Xist Foci per Cell') + 
  ylab("Percent") + 
  coord_cartesian(xlim = c(0,5))+
  scale_x_continuous(breaks = 0:5) +
  scale_y_continuous(limits = c(0, 100))+
  geom_errorbar(aes(ymin = ymin,
                    ymax= ymax), 
                    colour="black", 
                    width = 0.2,
                    position = position_dodge(width = 0.9))+
  facet_grid(PatientNumber ~ Karyotype) +
  theme_bw()+
  theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 20), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 

MultiX_Xist_2

############## 
```
