---
title: "Data analysis for CTs ploting and statistical calculations"
author: "Sigal Shachar"
date: "December 27 2016"
output:
  html_document: default
  pdf_document: default
---

### Introduction

This script analyzes data obtained by imaging primary human fibroblasts stained with chromosome paints for chr X (green channel), Y (FarRed channel)  and 18 (Red channel). Cells were grown in PE-cellCarrierUltra 384 plates and imaged using the YOKOGAWA CV7000 microscope with a 60X-water or 40X-air objective. Images were imported into KNIME and analyzed and the results were exported as tab separated txt files.
The script reads the txt files and calculates several features in 2D and in 3D including: Number of CTs per nucleus, nucleus size, CT size, CT centroid/COM distance from border and biggest or smallest X CT ranked.
Finally, it calculates p values and difference between medians using Wilcoxon test for the centroid distance from border diatributions.

Load packages.
```{r}
library('plyr')
library('dplyr')
library('ggplot2')
library('stringr')
library('knitr')
library('SpatialTools')
library('reshape2')
library('DT')
library('data.table')
library('Hmisc')
```


EXP12 XYXIST
```{r ReadCsvFiles}

FR_Data_All_train_XYXist <- fread(file="../CSV_Files/EXP12_2D_XYXist/WellsC06toE08_EXP12_2D_Xist_FarRedProbeMeasurements.csv", check.names = T, showProgress = T)
  
R_Data_All_train_XYXist <- fread(file="../CSV_Files/EXP12_2D_XYXist/WellsC06toE08EXP12_2D_Y_RedProbeMeasurements.csv", check.names = T, showProgress = T)

G_Data_All_train_XYXist <- fread(file="../CSV_Files/EXP12_2D_XYXist/WellsC06toE08_EXP12_2D_X_GreenProbeMeasurementsWithXistID.csv", check.names = T, showProgress = T)

#AllColors_2D_XYXist <- rbind(FR_Data_All_train_XYXist, R_Data_All_train_XYXist, G_Data_All_train_XYXist)

#Add New Plate Column#
FR_Data_All_train_XYXist$EXPPlate<- "Exp12Xist"
R_Data_All_train_XYXist$EXPPlate<- "Exp12Xist"
G_Data_All_train_XYXist$EXPPlate<- "Exp12Xist"
#AllColors_2D_13$EXPPlate<- "Exp12Xist"
  
```


Operations to filter out cells that have more CTs than expected. Also generates a data table that contains only nuclei that have the exact number of chromosomes CTs as expected by karyotype in 2D.
```{r filter}
#Columns to retain
keep1 <- c(5, 7, 14:15, 17:23, 27, 77, 90:95, 115:130, 125:151)
keep2 <- c(5, 7, 14:15,17:21, 25, 75, 90:95, 115:128, 125:141)
G_Data_All_train_XYXist <- G_Data_All_train_XYXist[, keep1, with=FALSE]
R_Data_All_train_XYXist <- R_Data_All_train_XYXist[, keep2, with=FALSE]
FR_Data_All_train_XYXist <- FR_Data_All_train_XYXist[, keep2, with=FALSE]

#Generates a new data table that counts the number of CTs per nucleus 
cell_G_12Xist <- G_Data_All_train_XYXist[,.(ct_number = .N),by = .(Well.Position, FieldNumber, Karyotype, NucleusID)]
cell_R_12Xist <- R_Data_All_train_XYXist[,.(ct_number = .N),by = .(Well.Position, FieldNumber, Karyotype, NucleusID)]
cell_FR_12Xist <- FR_Data_All_train_XYXist[,.(ct_number = .N),by = .(Well.Position, FieldNumber, Karyotype, NucleusID)]

#Joins the 2 data tables together by CT, adding a column called ct_number
setkey(G_Data_All_train_XYXist, Well.Position, FieldNumber, Karyotype, NucleusID)
setkey(cell_G_12Xist, Well.Position, FieldNumber, Karyotype, NucleusID)
G_Data_CTs_12Xist_Tnumber <- G_Data_All_train_XYXist[cell_G_12Xist, nomatch = 0]

setkey(R_Data_All_train_XYXist, Well.Position, FieldNumber, Karyotype, NucleusID)
setkey(cell_R_12Xist, Well.Position, FieldNumber, Karyotype, NucleusID)
R_Data_CTs_12Xist_Tnumber <- R_Data_All_train_XYXist[cell_R_12Xist, nomatch = 0]

setkey(FR_Data_All_train_XYXist, Well.Position, FieldNumber, Karyotype, NucleusID)
setkey(cell_FR_12Xist, Well.Position, FieldNumber, Karyotype, NucleusID)
FR_Data_CTs_12Xist_Tnumber <- FR_Data_All_train_XYXist[cell_FR_12Xist, nomatch = 0]

#Generate a threshold table that determines the expected CT number per karyotype, then join this table with the previous table
Karyotypes_X <- G_Data_CTs_12Xist_Tnumber[, unique(Karyotype)]
thres_table_X = data.table(Karyotype = Karyotypes_X, threshold = c(2, 1, 2))
setkey(G_Data_CTs_12Xist_Tnumber,Karyotype)
setkey(thres_table_X,Karyotype)
G_Data_CTs_12Xist_Tnumber2 <- G_Data_CTs_12Xist_Tnumber[thres_table_X, nomatch = 0]

Karyotypes_Y <- R_Data_CTs_12Xist_Tnumber[, unique(Karyotype)]
thres_table_Y = data.table(Karyotype = Karyotypes_Y, threshold = c(1, 1))
setkey(R_Data_CTs_12Xist_Tnumber,Karyotype)
setkey(thres_table_Y,Karyotype)
R_Data_CTs_12Xist_Tnumber2 <- R_Data_CTs_12Xist_Tnumber[thres_table_Y, nomatch = 0]

Karyotypes_Xist <- FR_Data_CTs_12Xist_Tnumber[, unique(Karyotype)]
thres_table_Xist = data.table(Karyotype = Karyotypes_Xist, threshold = c(1, 1))
setkey(FR_Data_CTs_12Xist_Tnumber,Karyotype)
setkey(thres_table_Xist,Karyotype)
FR_Data_CTs_12Xist_Tnumber2 <- FR_Data_CTs_12Xist_Tnumber[thres_table_Xist, nomatch = 0]

#Generate 2 new data tables: one with the exact expected CT number and one with the expected number or smaller-
G_Data_CTs_12Xist_filter_exact <- G_Data_CTs_12Xist_Tnumber2[ct_number == threshold,]
R_Data_CTs_12Xist_filter_exact <- R_Data_CTs_12Xist_Tnumber2[ct_number == threshold,]
FR_Data_CTs_12Xist_filter_exact <- FR_Data_CTs_12Xist_Tnumber2[ct_number == threshold,]
#AllColors_2D_12Xist_exact <- rbind(G_Data_CTs_12Xist_filter_exact, R_Data_CTs_12Xist_filter_exact, FR_Data_CTs_12Xist_filter_exact)

#G_Data_CTs_12Xist_filter_equalOrLess <- G_Data_CTs_12Xist_Tnumber2[ct_number <= threshold,]
#R_Data_CTs_12Xist_filter_equalOrLess <- R_Data_CTs_12Xist_Tnumber2[ct_number <= threshold,]
#FR_Data_CTs_12Xist_filter_equalOrLess <- FR_Data_CTs_12Xist_Tnumber2[ct_number <= threshold,]
#AllColors_2D_12Xist_equalorless <- rbind(G_Data_CTs_12Xist_filter_equalOrLess, R_Data_CTs_12Xist_filter_equalOrLess, FR_Data_CTs_12Xist_filter_equalOrLess)

```


Box Plot of Normalized Number of Xist pixels in the X segmented mask and Scatter Plot of Normalized Number of Xist pixels in the X segmented mask vs. X CT Size
```{r Xistscatterandboxplot, fig.width = 16}
G_Data_CTs_12Xist_filter_exact_XX <- G_Data_CTs_12Xist_filter_exact [Karyotype =='XX', ]
G_Data_CTs_12Xist_filter_exact_XX <- transform(G_Data_CTs_12Xist_filter_exact_XX, Norm.XistPixelsInXMask =(XistPixelsInXMask / Size..Geometric.Features.2D.)*100)

#Scatter Plot of the Number of Xist pixels in the X segmented mask vs. X CT Size
g <- ggplot(G_Data_CTs_12Xist_filter_exact_XX, aes(x=XistPixelsInXMask, y = Size..Geometric.Features.2D._CT , fill=InactiveFlag)) 
g + geom_point(aes(color=InactiveFlag)) + 
  #geom_smooth(method=lm, se=FALSE) +
  facet_wrap(~ Karyotype, ncol=3) +
  ggtitle(' ')+
  ylab( 'X CT Area (Pixels)')+
  xlab( 'Xist Pixels')+
  theme(legend.position = "right", legend.text=element_text(size=18, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 18), axis.title = element_text(size = 18, face="bold"),text = element_text(size = 18), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=18,face="bold"), axis.text.y = element_text(colour="grey20",size=18,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA))  

#Box Plot of Normalized Number of X CT Size vs. X-Chromoome State
g_ActvsInac <- ggplot(G_Data_CTs_12Xist_filter_exact_XX, aes(x=InactiveFlag, y = Size..Geometric.Features.2D._CT, fill=InactiveFlag)) 
g_ActvsInac + geom_boxplot(outlier.size = 0, notch= TRUE)+ 
  #geom_point(position=position_jitterdodge(), size = 0.15)+
  #ggtitle('Normalized Number of Xist pixels in the X segmented mask')+
  ylab( 'Normalized Xist Pixels')+
  #ylim(c(0, .0385))+
  theme(legend.position = "right", legend.text=element_text(size=18, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 18), axis.title = element_text(size = 18, face="bold"),text = element_text(size = 18), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=18,face="bold"), axis.text.y = element_text(colour="grey20",size=18,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA))  

```

Active X vs. Inactive X Centroid
```{r XCentroidXaXi, fig.width = 16}
X.centroid.2D <- ggplot(G_Data_CTs_12Xist_filter_exact_XX, aes(x = Normalized.Centriod.DistanceMap, group = InactiveFlag, color = InactiveFlag))+ 
                 geom_density(size=1, adjust = 1.2) +
                 scale_color_brewer(palette = "Dark2") +
                 ylab('Density') +
                 theme_bw()+
                 theme(text = element_text(size=20),
               axis.text.x = element_text(angle=0, size=20))+
         #axis.text.y = element_text(colour="white"),
         #axis.title = element_text(colour="white"),
               #legend.Position = "top")+
              xlab('X Rank#1 centroid distance from border')
print(X.centroid.2D)

#Calculating the difference between the 2 CDFs using Kolmogorov-Smirnov (KS) test

Xi <- G_Data_CTs_12Xist_filter_exact_XX[InactiveFlag == 'Inactive', Normalized.Centriod.DistanceMap]

Xa <- G_Data_CTs_12Xist_filter_exact_XX[InactiveFlag == '', Normalized.Centriod.DistanceMap]

KS.values <-ks.test(Xi,Xa)



```


Shell analyis of Acitive and Inactive X EXP 12
```{r ShellAnalysis, fig.width = 16}

G_Data_CTs_12Xist_filter_exact_XX$Pct.Shell1 <- (G_Data_CTs_12Xist_filter_exact_XX$NumPixelsdistantShell1 / G_Data_CTs_12Xist_filter_exact_XX$NumPixelsAlldistantShells ) 
G_Data_CTs_12Xist_filter_exact_XX$Pct.Shell2 <- (G_Data_CTs_12Xist_filter_exact_XX$NumPixelsdistantShell2 / G_Data_CTs_12Xist_filter_exact_XX$NumPixelsAlldistantShells ) 
G_Data_CTs_12Xist_filter_exact_XX$Pct.Shell3 <- (G_Data_CTs_12Xist_filter_exact_XX$NumPixelsdistantShell3 / G_Data_CTs_12Xist_filter_exact_XX$NumPixelsAlldistantShells ) 
G_Data_CTs_12Xist_filter_exact_XX$Pct.Shell4 <- (G_Data_CTs_12Xist_filter_exact_XX$NumPixelsdistantShell4 / G_Data_CTs_12Xist_filter_exact_XX$NumPixelsAlldistantShells ) 
G_Data_CTs_12Xist_filter_exact_XX$Pct.Shell5 <- (G_Data_CTs_12Xist_filter_exact_XX$NumPixelsdistantShell5 / G_Data_CTs_12Xist_filter_exact_XX$NumPixelsAlldistantShells ) 

G_Data_melt_Xist <- melt(G_Data_CTs_12Xist_filter_exact_XX, measure.vars = c("Pct.Shell1", "Pct.Shell2", "Pct.Shell3", "Pct.Shell4", "Pct.Shell5" ),
variable.name = "Shell.Number", na.rm = FALSE, value.name = "value", factorsAsStrings = TRUE)



G_Pct_Per.Shell_Xist <- G_Data_melt_Xist[, .(ave_perc = mean(value))
                      , by = .(Well.Position, Karyotype, Shell.Number, InactiveFlag)]


G_Shells_plot_Xist <- ggplot(G_Pct_Per.Shell_Xist,aes(Shell.Number, ave_perc, colour = InactiveFlag )) +  
  stat_summary(fun.data = mean_cl_normal, position = position_dodge(0.5), size = 2)+
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0, 0.5))+
  #ggtitle('XX')+
                 ylab('Average Percent of X CT in Equidistant Shell') +
                 theme_bw()+
                theme(legend.position = "right", legend.text=element_text(size=25, face="bold"), plot.title = element_text(hjust = 0.5), axis.text = element_text(size = 25), axis.title = element_text(size = 25, face="bold"),text = element_text(size = 25), panel.background = element_rect(fill='white', colour='black'), axis.text.x= element_text(colour="grey20",size=20,face="bold"), axis.text.y = element_text(colour="grey20",size=20,face="bold"), panel.border = element_rect(linetype = "dashed", fill = NA)) 
 
print(G_Shells_plot_Xist)

```


Calculate p-values comparing the negative controls with the samples using the Mann-Whitney test. No multiple testing correction is employed. Run only once
```{r  Mann1, results='hide'}
pValues <- function(a, b){
            test.results <- wilcox.test(a,b)
            test.results$p.value
}
```


Create an additional table for p-values according to the Mann-Whitney tests (one sample vs each of the other ones) 
```{r createPvalueTables, results='hide'}
XX.XistIntensity.XivsXa <- G_Data_CTs_12Xist_filter_exact_XX[InactiveFlag == "Inactive", Norm.XistPixelsInXMask]

pValues.XistIntensity.XivsXa <- G_Data_CTs_12Xist_filter_exact_XX[, 
                     list(mannWhit.pValue = pValues(XX.XistIntensity.XivsXa, Norm.XistPixelsInXMask),
                          median.XistIntensity.XivsXa = median(Norm.XistPixelsInXMask)),
                     by = InactiveFlag]


XX.CT.Area.XistIntensity.XivsXa <- G_Data_CTs_12Xist_filter_exact_XX[InactiveFlag == "Inactive", Size..Geometric.Features.2D._CT]

pValues.CT.Area.XistIntensity.XivsXa <- G_Data_CTs_12Xist_filter_exact_XX[, 
                     list(mannWhit.pValue = pValues(XX.CT.Area.XistIntensity.XivsXa, Size..Geometric.Features.2D._CT),
                          median.CT.Area.XistIntensity.XivsXa = median(Size..Geometric.Features.2D._CT)),
                     by = InactiveFlag]

```

Document the information about the analysis session
```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```